---
title: "Data Appendix - WVS variables after data preparation"
author: "Remizova Alisa"
output: pdf_document
---

This is a description of the individual-level data after preparatory analysis. The dataset is the combined data of the two latest rounds of the World Values Survey (WVS). Each row is individual observation (respondent).

There are the following changes compared to the original WVS data:

1. For the identification as a religious person item, the "non-religious" and "atheist" response options are collapsed into a single category "not religious" category so that the variable differentiates between religious and non-religious respondents.
2. The belonging to a denomination indicator is recoded into a binary variable corresponding to affiliation and non-affiliation with a denomination.
3. The response options of all indicators are recoded so that higher scores correspond to higher religiosity.
4. All variables except gender are converted from factor to numeric format that is necessary for the further analysis.

```{r prep, echo = FALSE, message = FALSE, warning = FALSE}
# Please run the code for the data preparation (the same as in the master script)

library(car)
library(foreign)
library(haven)
library(dplyr)
library(mice)
library(LittleHelpers)
library(MplusAutomation)
library(readxl)
library(gdata)
library(kableExtra) 
library(sna)
library(reshape2)

# Upload two functions written for the current analysis
source("./01_Scripts/02_AnalysisScripts/AddFunctions.R")

# DATA PREPARATION

# WVS 7 

# Religiosity indicators:
## Q6 - For each of the following, indicate how important it is in your life - Religion
## Q64 - For each one, could you tell me how much confidence you have in them. The Churches
## Q289 - Do you belong to a religion or religious denomination? 
## Q171 - Apart from weddings and funerals, about how often do you attend religious services these days?
## Q172 - Apart from weddings and funerals, about how often do you pray?
## Q173 - Would you say you are... religious / not a religious person / an atheist

## Q94 - For each organization, could you tell me whether you are….? 
### active / inactive member / do not belong. Church or religious organization
## Q165 - Which, if any, of the following do you believe in? God?
## Q167 - Hell
## Q164 - How important is God in your life?

# Missing data correlates:
## Q260 - Gender: Male Female 
## Q262 - You are ____ years old 
## Q288 - On this card is an income scale on which 1 indicates the lowest income group and 10 the highest income group
### in your country. We would like to know in what group your household is. 
### from Lower step to Tenth step 
## Q275 - What is the highest educational level that you have attained?
### from Early childhood education / no education
### to Doctoral or equivalent

# Other variables:
## B_COUNTRY - Country name
## N_REGION_ISO - Country-specific region (necessary for Germany)
## A_YEAR - Survey year

# Upload country codes
codes <- read_excel("./02_Data/01_InputData/CountryInfo.xlsx", sheet = "Country codes")

# Read data
WVS7 <- read.spss("./02_Data/01_InputData/WVS_Cross-National_Wave_7_sav_v2_0.sav", 
                  use.value.labels = T, to.data.frame = T, 
                  use.missings = T)
## Ignore the warnings

# Set the same country names in WVS7 as in WVS6:
levels(WVS7$B_COUNTRY)[levels(WVS7$B_COUNTRY)=="Taiwan ROC"] <- "Taiwan"
levels(WVS7$B_COUNTRY)[levels(WVS7$B_COUNTRY)=="Hong Kong SAR"] <- "Hong Kong"

# Merge with country codes
WVS7 <- merge(WVS7, codes, by.x = c("B_COUNTRY"), by.y = c("country"),  all.x = T)

# Select only necessary variables
rel_data <- select(WVS7, c(B_COUNTRY, N_REGION_ISO, Q6, Q94, Q64, Q289, Q171, Q172, Q173, Q165, Q167, 
                           Q164, Q260, Q262, Q288, Q275, A_YEAR, code)) 

# Set the following column names for religiosity indicators:
## Importance of religion = imprel
## Membership in a religious organisation = member
## Confidence in institutions = confidence
## Belonging to a denomination = belong
## Frequency of attendance = attend
## Frequency of praying = pray
## Identification as religious person = person
## Belief in God = bgod
## Belief in hell = bhell
## Importance of God = impgod
colnames(rel_data) <- c("country", "region", "imprel", "member", "confidence", "belong", "attend",
                        "pray", "person", "bgod", "bhell", "impgod", 
                        "gender", "age", "income", "education", "year", "code")

# Make two separate samples for Germany: East and West
Germany <- rel_data[rel_data$country == "Germany", ]
Germany$region <- droplevels(Germany$region)
Germany$country <- droplevels(Germany$country)

# Recode and drop Berlin
Germany$country <- Recode(
  Germany$region,
  recodes = "'DE-MV Mecklenburg-Western Pomerania' = 'Germany East';
  'DE-BB Brandenburg' = 'Germany East';
  'DE-SN Saxony' = 'Germany East';
  'DE-ST Saxony-Anhalt' = 'Germany East';
  'DE-TH Thuringia' = 'Germany East';
  'DE-BE Berlin' = NA;
  else = 'Germany West'",
  as.factor = T)

Germany <- Germany[!is.na(Germany$country), ]

# Add to the main dataset
rel_data <- rbind(rel_data, Germany)
rel_data <- subset(
  rel_data, subset = !(rel_data$country == "Germany"))
rel_data$region <- NULL
rm(Germany)

# Add country-specific data files for Kenya, Armenia, Mongolia, 
## Venezuela, Maldives, Northern Ireland, Great Britain, Czechia, and Slovakia from WVS7 last release
## (countries not included in the second WVS 7 release and WVS 6)
## with haven package so that the variables' values are trimmed

WVS7_05 <- read_spss("./02_Data/01_InputData/WVS_Cross-National_Wave_7_spss_v5_0.sav")

# Select columns
rel_data_05 <- select(WVS7_05, c(B_COUNTRY, Q6, Q94, Q64, Q289, Q171, Q172, Q173, Q165,
                                 Q167, Q164, Q260, Q262, Q288, Q275, A_YEAR))

colnames(rel_data_05) <- c("country", "imprel", "member", "confidence", "belong", "attend",
                           "pray", "person", "bgod", "bhell", "impgod", 
                           "gender", "age", "income", "education", "year")

# Recode to labelled factors
for (item in c("country", "imprel", "member", "confidence", "belong", "attend",
               "pray", "person", "bgod", "bhell", "impgod", 
               "gender", "age", "income", "education", "year")) {
  rel_data_05[, item] <- as_factor(rel_data_05[, item])
  rel_data_05[, item] <- droplevels(rel_data_05[, item])
  
}

# Subset countries
rel_data_05 <- subset(rel_data_05, subset = rel_data_05$country %in% 
                        c("Northern Ireland", "Czechia", "Slovakia", "Great Britain", "Kenya", 
                          "Armenia", "Mongolia", "Venezuela", "Maldives"))
rel_data_05$country <- droplevels(rel_data_05$country)

# Merge with country codes
rel_data_05 <- merge(rel_data_05, codes, by = c("country"),  all.x = T)

# Recode income because of different coding 
rel_data$income <- as.numeric(rel_data$income)
rel_data_05$income <- as.numeric(rel_data_05$income)

# Combine WVS 7 datasets
rel_data <- rbind(rel_data, rel_data_05)
## 61 countries - do not count "Germany"

# -------------
  
# WVS 6

# Religiosity indicators:
## V9 - For each of the following, indicate how important it is in your life: Religion
## V108 - For each one, could you tell me how much confidence you have in them. The Churches
## V144 - Do you belong to a religion or religious denomination? 
## V145 - Apart from weddings and funerals, about how often do you attend religious services these days?
## V146 - Apart from weddings and funerals, about how often do you pray?
## V147 - Would you say you are... religious / not a religious person / an atheist

## V25 - For each organization, could you tell me whether you are….? 
### active / inactive member / do not belong. Church or religious organization
## V148 - Do you believe in God?
## V149 - Do you believe in hell? 
## V152 - How important is God in your life?

# Missing data correlates:
# V240 - Gender: Male Female 
# V242 - You are ____ years old 
# V239 - On this card is an income scale on which 1 indicates the lowest income group and 10 the highest
## income group in your country. We would like to know in what group your household is. 
## from Lower step to Tenth step
# V248 - What is the highest educational level that you have attained?
## from No formal education to University - level education, with degree 

# Other variables:
## V2 - Country name

# Read data
WVS6 <- read.spss("./02_Data/01_InputData/WV6_Data_Spss_v20180912.sav", use.value.labels = T, 
                  to.data.frame = T, use.missings = T)
## Ignore the warnings

# Upload survey year
WVS6_year <- read_excel("./02_Data/01_InputData/CountryInfo.xlsx", sheet = "Survey year")

# Merge with country codes and survey year
WVS6 <- merge(WVS6, WVS6_year, by.x = c("V2"), by.y = c("country"), all.x = T)
WVS6 <- merge(WVS6, codes, by.x = c("V2"), by.y = c("country"),  all.x = T)

# Select only necessary variables
rel_data_WVS6 <- select(WVS6, c(V2, V9, V25, V108, V144:V149, V152, 
                                V240, V242, V239, V248, year, code))

colnames(rel_data_WVS6) <- c("country", "imprel", "member", "confidence", "belong", "attend",
                             "pray", "person", "bgod", "bhell", "impgod", 
                             "gender", "age", "income", "education", "year", "code")

# Subset countries that did not participate in WVS 7
rel_data_WVS6 <- subset(rel_data_WVS6, subset = 
                          !(rel_data_WVS6$country %in% levels(rel_data$country)))
rel_data_WVS6$country <- droplevels(rel_data_WVS6$country)
# 24 countries

# -------------

# Harmonize "education" indicator for two waves
## WVS 6
levels(rel_data_WVS6$education)[levels(rel_data_WVS6$education) == "No formal education"|
                                  levels(rel_data_WVS6$education) =="Incomplete primary school"] <- 
  "Early childhood education (ISCED 0) / no education"
levels(rel_data_WVS6$education)[levels(rel_data_WVS6$education) == "Complete primary school"] <- "Primary education (ISCED 1)"
levels(rel_data_WVS6$education)[levels(rel_data_WVS6$education) == "Incomplete secondary school: technical/ vocational type"|
                                  levels(rel_data_WVS6$education) =="Incomplete secondary school: university-preparatory type"] <- 
  "Lower secondary education (ISCED 2)"
levels(rel_data_WVS6$education)[levels(rel_data_WVS6$education) == "Complete secondary school: technical/ vocational type"|
                                  levels(rel_data_WVS6$education) == "Complete secondary school: university-preparatory type"|
                                  levels(rel_data_WVS6$education) == "Some university-level education, without degree"] <- 
  "Upper secondary / short tertiary education"

## WVS 7
levels(rel_data$education)[levels(rel_data$education) == "Upper secondary education (ISCED 3)"|
                                  levels(rel_data$education) =="Post-secondary non-tertiary education (ISCED 4)"|
                             levels(rel_data$education) =="Short-cycle tertiary education (ISCED 5)"] <- 
  "Upper secondary / short tertiary education"
levels(rel_data$education)[levels(rel_data$education) == "Bachelor or equivalent (ISCED 6)"|
                             levels(rel_data$education) == "Master or equivalent (ISCED 7)"|
                             levels(rel_data$education) == "Doctoral or equivalent (ISCED 8)"] <- 
  "University - level education, with degree"
rel_data$education <- droplevels(rel_data$education)

# Convert praying, belonging, and membership into numeric class 
## for each wave separately because of the different coding of levels
# Also convert year and age to numeric for WVS 7 and age for WVS 6 
# Also convert income to numeric for WVS 6 because of slightly different coding

for (item in c("member", "belong", "pray")) {
  rel_data[, item] <- as.numeric(rel_data[, item])
}

for (item in c("member", "belong", "pray", "income")) {
  rel_data_WVS6[, item] <- as.numeric(rel_data_WVS6[, item])
}

for (item in c("age", "year")) {
  rel_data[, item] <- as.numeric(as.character(rel_data[, item]))
}

rel_data_WVS6$age <- as.numeric(as.character(rel_data_WVS6$age))

# Combine two waves
rel_data <- rbind(rel_data, rel_data_WVS6)
rel_data$country <- droplevels(rel_data$country)
# 85 countries in total

# -------------

# Recode the remaining variables into numeric
for (item in c("imprel", "confidence", "attend", "person", "bgod", "bhell", "impgod", 
               "education")) {
  rel_data[, item] <- as.numeric(rel_data[, item])
}

# Reverse recode all variables except impgod and member
## They do not need to be recoded - higher scores already correspond to higher religiosity
for (item in c("imprel", "confidence")) {
  rel_data[,item] <- Recode(rel_data[,item], rec= "1=4; 2=3; 3=2; 4=1; else=NA")
}

for (item in c("bgod", "bhell")) {
  rel_data[,item] <- Recode(rel_data[,item], rec= "1=2; 2=1; else=NA")
}

rel_data$attend <- Recode(rel_data$attend, rec = "1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
rel_data$pray <- Recode(rel_data$pray, rec = "1=8; 2=7; 3=6; 4=5; 5=4; 6=3; 7=2; 8=1; else=NA")

# Make person binary
rel_data$person <- Recode(rel_data$person, rec = "1=2; 2=1; 3=1; else=NA")

# Make belonging binary
rel_data$belong <- ifelse(rel_data$belong == "1", 1, 2)

```


# Main variables 

The main variables were used in the analysis presented in the paper.

## Importance of religion

Question wording: "For each of the following, indicate how important it is in your life - Religion"

WVS name: Q6 in WVS 7 and V9 in WVS 6

Code name: imprel

The variable is the reversed coded version of the original variable so that higher scores correspond to higher importance of religion. 

Final coding: 1 = Not at all important; 2 = Not very important; 3 = Rather important; 4 = Very important

```{r imprel, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyr)

# Create count table by country, with a column for missing values
imprel_tab <- rel_data %>%
  group_by(country) %>%
  count(imprel) %>%
  spread(imprel, n)

colnames(imprel_tab)[6] <- "Missing"

# Make the columns with N observations
imprel_tab$N <- rowSums(imprel_tab[, 2:6], na.rm = T)

# Make the missings in percent
imprel_tab$Missing <- round(
  imprel_tab$Missing/rowSums(imprel_tab[, 2:6], na.rm = T)*100, 1)

# Replace NAs in the table
imprel_tab <- imprel_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

# Rename country column with capital letter
colnames(imprel_tab)[1] <- "Country"

# Order by country
imprel_tab$Country <- trim(imprel_tab$Country)
imprel_tab <- imprel_tab[order(imprel_tab$Country), ] 

kable(imprel_tab, "latex", booktabs = T, longtable = T, row.names = F, digits = 2,
      align = "lcccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations"
  )

```

## Confidence in institutions

Question wording: "I am going to name a number of organizations. For each one, could you tell me how much confidence you have in them? The Churches"

WVS name: Q64 in WVS 7 and V108 in WVS 6

Code name: confidence

The variable is the reversed coded version of the original variable so that higher scores correspond to higher confidence in institutions. 

Final coding: 1 = None at all important; 2 = Not very much; 3 = Quite a lot; 4 = A great deal

```{r confidence, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
conf_tab <- rel_data %>%
  group_by(country) %>%
  count(confidence) %>%
  spread(confidence, n)

colnames(conf_tab)[6] <- "Missing"

conf_tab$N <- rowSums(conf_tab[, 2:6], na.rm = T)

conf_tab$Missing <- round(
  conf_tab$Missing/rowSums(conf_tab[, 2:6], na.rm = T)*100, 1)

conf_tab <- conf_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(conf_tab)[1] <- "Country"

conf_tab$Country <- trim(conf_tab$Country)
conf_tab <- conf_tab[order(conf_tab$Country), ] 

kable(conf_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Belonging to a denomination

Question wording: "Do you belong to a religion or religious denomination? If yes, which one?"

WVS name: Q289 in WVS 7 and V144 in WVS 6

Code name: belong

The variable is the recoded (binary) version of the original variable so that it corresponds to affiliation and non-affiliation with a denomination. 

Final coding: 1 = No, do not belong to a denomination; 2 = Yes, belong to a denomination

```{r belong, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
belong_tab <- rel_data %>%
  group_by(country) %>%
  count(belong) %>%
  spread(belong, n)

colnames(belong_tab)[4] <- "Missing"

belong_tab$N <- rowSums(belong_tab[, 2:4], na.rm = T)

belong_tab$Missing <- round(
  belong_tab$Missing/rowSums(belong_tab[, 2:4], na.rm = T)*100, 1)

belong_tab <- belong_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(belong_tab)[1] <- "Country"

belong_tab$Country <- trim(belong_tab$Country)
belong_tab <- belong_tab[order(belong_tab$Country), ] 

kable(belong_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```


## Frequency of religious attendance

Question wording: "Apart from weddings and funerals, about how often do you attend religious services these days?"

WVS name: Q171 in WVS 7 and V145 in WVS 6

Code name: attend

The variable is the reversed coded version of the original variable so that higher scores correspond to higher frequency of religious attendance. 

Final coding: 1 = Never, practically; 2 = Less often; 3 = Once a year; 4 = Only on special holy days; 5 = Once a month; 6 = Once a week; 7 = More than once a week

```{r attend, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
# Create  table by country, with mean, standard deviation, 
attend_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(attend, na.rm = T), 2), 
            SD = round(sd(attend, na.rm = T), 2),
            Range = paste(min(attend, na.rm = T), max(attend, na.rm = T), sep = "-"),
            Missing = sum(is.na(attend)),
            N = length(attend))

# Substitute no missing values with NA
attend_tab$Missing[attend_tab$Missing == 0] <- NA

# Make the missings in percent
attend_tab$Missing <- round(attend_tab$Missing/attend_tab$N*100, 1)

# Replace NAs in the table 
attend_tab <- attend_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
attend_tab$Range[attend_tab$Range == "Inf--Inf"] <- "-"

# Rename country column with capital letter
colnames(attend_tab)[1] <- "Country"

# Order by country
attend_tab$Country <- trim(attend_tab$Country)
attend_tab <- attend_tab[order(attend_tab$Country), ] 

kable(attend_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Frequency of praying

Question wording: "Apart from weddings and funerals, about how often do you pray?"

WVS name: Q172 in WVS 7 and V146 in WVS 6

Code name: pray

The variable is the reversed coded version of the original variable so that higher scores correspond to higher frequency of praying. 

Final coding: 1 = Never, practically never; 2 = Less often (Less often than once a year in WVS 6); 3 = Once a year; 4 = Only on special holy days; 5 = Only when attending religious services; 6 = Several times each week; 7 = Once a day; 8 = Several times a day

```{r pray, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
pray_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(pray, na.rm = T), 2), 
            SD = round(sd(pray, na.rm = T), 2),
            Range = paste(min(pray, na.rm = T), max(pray, na.rm = T), sep = "-"),
            Missing = sum(is.na(pray)),
            N = length(pray))

pray_tab$Missing[pray_tab$Missing == 0] <- NA
pray_tab$Missing <- round(pray_tab$Missing/pray_tab$N*100, 1)

pray_tab <- pray_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
pray_tab$Range[pray_tab$Range == "Inf--Inf"] <- "-"

colnames(pray_tab)[1] <- "Country"

pray_tab$Country <- trim(pray_tab$Country)
pray_tab <- pray_tab[order(pray_tab$Country), ] 

kable(pray_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Identification as a religious person

Question wording: "Independently of whether you attend religious services or not, would you say you are:"

WVS name: Q173 in WVS 7 and V147 in WVS 6

Code name: person

The variable is the recoded (binary) version of the original variable. Thus, the “non-religious” and “atheist” response options are collapsed into the a single  “not religious” category so that the variable differentiates between religious and non-religious respondents. Moreover, the response options are reversed so that higher scores correspond to identification as a religious person.  

Final coding: 1 = Not religious person; 2 = A religious person

```{r person, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
person_tab <- rel_data %>%
  group_by(country) %>%
  count(person) %>%
  spread(person, n)

colnames(person_tab)[4] <- "Missing"

person_tab$N <- rowSums(person_tab[, 2:4], na.rm = T)

person_tab$Missing <- round(
  person_tab$Missing/rowSums(person_tab[, 2:4], na.rm = T)*100, 1)

person_tab <- person_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(person_tab)[1] <- "Country"

person_tab$Country <- trim(person_tab$Country)
person_tab <- person_tab[order(person_tab$Country), ] 

kable(person_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```


# Other variables

These variables were used only to impute the missing values of the main variables

## Importance of God

Question wording: "How important is God in your life?"

WVS name: Q164 in WVS 7 and V152 in WVS 6

Code name: impgod

This is the original version of the variable.

Coding: 1 = Not at all important; 2 = 2; 3 = 3; 4 = 4; 5 = 5; 6 = 6; 7 = 7; 8 = 8; 9 = 9; 10 = Very important

```{r impgod, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
impgod_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(impgod, na.rm = T), 2), 
            SD = round(sd(impgod, na.rm = T), 2),
            Range = paste(min(impgod, na.rm = T), max(impgod, na.rm = T), sep = "-"),
            Missing = sum(is.na(impgod)),
            N = length(impgod))

impgod_tab$Missing[impgod_tab$Missing == 0] <- NA
impgod_tab$Missing <- round(impgod_tab$Missing/impgod_tab$N*100, 1)

impgod_tab <- impgod_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
impgod_tab$Range[impgod_tab$Range == "Inf--Inf"] <- "-"

colnames(impgod_tab)[1] <- "Country"

impgod_tab$Country <- trim(impgod_tab$Country)
impgod_tab <- impgod_tab[order(impgod_tab$Country), ] 

kable(impgod_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Membership in an organisation

Question wording: "For each organization, could you tell me whether you are….? Church or religious organization"

WVS name: Q94 in WVS 7 and V25 in WVS 6

Code name: member

This is the original version of the variable.

Coding: 1 = Do not belong (Not a member in WVS 6); 2 = Inactive member; 3 = Active member

```{r member, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
member_tab <- rel_data %>%
  group_by(country) %>%
  count(member) %>%
  spread(member, n)

colnames(member_tab)[5] <- "Missing"

# make the columns with N observations
member_tab$N <- rowSums(member_tab[, 2:5], na.rm = T)

# make the missings in percent
member_tab$Missing <- round(
  member_tab$Missing/rowSums(member_tab[, 2:4], na.rm = T)*100, 1)

member_tab <- member_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(member_tab)[1] <- "Country"

member_tab$Country <- trim(member_tab$Country)
member_tab <- member_tab[order(member_tab$Country), ] 

kable(member_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Belief in God

Question wording: "Which, if any, of the following do you believe in? God?" in WVS 7 and "Do you believe in God?" in WVS 6

WVS name: Q165 in WVS 7 and V148 in WVS 6

Code name: bgod

The variable is the reversed coded version of the original variable so that it corresponds to non-belief and belief in God. 

Final coding: 1 = No; 2 = Yes

```{r bgod, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
bgod_tab <- rel_data %>%
  group_by(country) %>%
  count(bgod) %>%
  spread(bgod, n)

colnames(bgod_tab)[4] <- "Missing"

bgod_tab$N <- rowSums(bgod_tab[, 2:4], na.rm = T)

bgod_tab$Missing <- round(
  bgod_tab$Missing/rowSums(bgod_tab[, 2:4], na.rm = T)*100, 1)

bgod_tab <- bgod_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(bgod_tab)[1] <- "Country"

bgod_tab$Country <- trim(bgod_tab$Country)
bgod_tab <- bgod_tab[order(bgod_tab$Country), ] 

kable(bgod_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Belief in hell

Question wording: "Which, if any, of the following do you believe in? Hell?" in WVS 7 and "Do you believe in hell?" in WVS 6

WVS name: Q167 in WVS 7 and V149 in WVS 6

Code name: bhell

The variable is the reversed coded version of the original variable so that it corresponds to non-belief and belief in hell 

Final coding: 1 = No; 2 = Yes

```{r bhell, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
bhell_tab <- rel_data %>%
  group_by(country) %>%
  count(bhell) %>%
  spread(bhell, n)

colnames(bhell_tab)[4] <- "Missing"

bhell_tab$N <- rowSums(bhell_tab[, 2:4], na.rm = T)

bhell_tab$Missing <- round(
  bhell_tab$Missing/rowSums(bhell_tab[, 2:4], na.rm = T)*100, 1)

bhell_tab <- bhell_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(bhell_tab)[1] <- "Country"

bhell_tab$Country <- trim(bhell_tab$Country)
bhell_tab <- bhell_tab[order(bhell_tab$Country), ] 

kable(bhell_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Age

Question wording: "You are ____ years old"

WVS name: Q262 in WVS 7 and V242 in WVS 6

Code name: age

This is the original version of the variable.

```{r age, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
age_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(age, na.rm = T), 2), 
            SD = round(sd(age, na.rm = T), 2),
            Range = paste(min(age, na.rm = T), max(age, na.rm = T), sep = "-"),
            Missing = sum(is.na(age)),
            N = length(age))

age_tab$Missing[age_tab$Missing == 0] <- NA
age_tab$Missing <- round(age_tab$Missing/age_tab$N*100, 1)

age_tab <- age_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
age_tab$Range[age_tab$Range == "Inf--Inf"] <- "-"

colnames(age_tab)[1] <- "Country"

age_tab$Country <- trim(age_tab$Country)
age_tab <- age_tab[order(age_tab$Country), ] 

kable(age_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Gender

Question wording: "Gender"

WVS name: Q260 in WVS 7 and V240 in WVS 6

Code name: gender

This is the original version of the variable.

```{r gender, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
gender_tab <- rel_data %>%
  group_by(country) %>%
  count(gender) %>%
  spread(gender, n)

colnames(gender_tab)[4] <- "Missing"

gender_tab$N <- rowSums(gender_tab[, 2:4], na.rm = T)

gender_tab$Missing <- round(
  gender_tab$Missing/rowSums(gender_tab[, 2:4], na.rm = T)*100, 1)

gender_tab <- gender_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")

colnames(gender_tab)[1] <- "Country"

gender_tab$Country <- trim(gender_tab$Country)
gender_tab <- gender_tab[order(gender_tab$Country), ] 

kable(gender_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lcccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

## Education

Question wording: "What is the highest educational level that you have attained?"

WVS name: Q275 in WVS 7 and V248 in WVS 6

Code name: education

The variable is the reversed coded version of the original variable so that the different response options in the two survey waves are harmonized. 

In the WVS 6, the "No formal education" and "Incomplete primary school"  response options are collapsed into a single "Early childhood education (ISCED 0) / no education" category; the "Incomplete secondary school: technical/ vocational type" and "Incomplete secondary school: university-preparatory type" response options are collapsed into a single "Lower secondary education (ISCED 2)" category; the "Complete secondary school: technical/ vocational type", "Complete secondary school: university-preparatory type", and "Some university-level education, without degree" response options are collapsed into a single "Upper secondary / short tertiary education" category. Moreover, the "Complete primary school" category is recoded into the "Primary education (ISCED 1)" category. 

In the WVS 7, the "Upper secondary education (ISCED 3)", "Post-secondary non-tertiary education (ISCED 4)", and "Short-cycle tertiary education (ISCED 5)"
response options are collapsed into a single "Upper secondary / short tertiary education" category; the "Bachelor or equivalent (ISCED 6)", "Master or equivalent (ISCED 7)", and "Doctoral or equivalent (ISCED 8)" response options are collapsed into a single "University - level education, with degree" category.

Higher scores correspond to higher level of education. 

Final coding: 1 = Early childhood education (ISCED 0) / no education; 2 = Primary education (ISCED 1); 3 = Lower secondary education (ISCED 2); 4 = Upper secondary / short tertiary education; 5 = University - level education, with degree

```{r education, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
educ_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(education, na.rm = T), 2), 
            SD = round(sd(education, na.rm = T), 2),
            Range = paste(min(education, na.rm = T), max(education, na.rm = T), sep = "-"),
            Missing =sum(is.na(education)),
            N = length(education))

educ_tab$Missing[educ_tab$Missing == 0] <- NA
educ_tab$Missing <- round(educ_tab$Missing/educ_tab$N*100, 1)

educ_tab <- educ_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
educ_tab$Range[educ_tab$Range == "Inf--Inf"] <- "-"

colnames(educ_tab)[1] <- "Country"

educ_tab$Country <- trim(educ_tab$Country)
educ_tab <- educ_tab[order(educ_tab$Country), ] 

kable(educ_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```


## Income

Question wording: "On this card is an income scale on which 1 indicates the lowest income group and 10 the highest income group in your country. We would like to know in what group your household is."

WVS name: Q288 in WVS 7 and V239 in WVS 6

Code name: income

This is the original version of the variable.

Coding: 1 = Lower step; 2 = Second step (second in the fifth WVS 7 release); 3 = Third step; 4 = Fourth step; 5 = Fifth step; 6 = Sixth step; 7 = Seventh step; 8 = Eight (Eigth in WVS 6) step; 9 = Nineth step; 10 = Tenth step

```{r income, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
income_tab <- rel_data %>%
  group_by(country) %>%
  summarise(Mean = round(mean(income, na.rm = T), 2), 
            SD = round(sd(income, na.rm = T), 2),
            Range = paste(min(income, na.rm = T), max(income, na.rm = T), sep = "-"),
            Missing = sum(is.na(income)),
            N = length(income))

income_tab$Missing[income_tab$Missing == 0] <- NA
income_tab$Missing <- round(income_tab$Missing/income_tab$N*100, 1)

income_tab <- income_tab %>%
  mutate_if(is.numeric , replace_na, replace = "-")
income_tab$Range[income_tab$Range == "Inf--Inf"] <- "-"

colnames(income_tab)[1] <- "Country"

income_tab$Country <- trim(income_tab$Country)
income_tab <- income_tab[order(income_tab$Country), ] 

kable(income_tab, "latex", booktabs = T, longtable = T, row.names = F,
      align = "lccccc") %>%
  kable_styling(latex_options = c("striped", "repeat_header"), full_width = T) %>%
  footnote(
    general = "SD = Standard deviation; Missing = Missing values, in %; N = Number of observations; - = No data"
  )
```

